Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-05 Paper/results.tex
typo: lower case for enthalpy

For both AMR-Wind and Nalu-Wind each time step is dominated by the linear solver work. 
A time step within AMR-Wind requires two poisson solves (MAC and nodal projection),
a tensor Helmholtz solve for Momentum equations, and two scalar Helmholtz solves 
(potential temperature equation and subgrid-scale kinetic energy equation).
Nalu-Wind is a fully implicit scheme and requires a non-linear Picard iteration for each time
step, in this work we use two Picard iterations for every time step.
Each Picard iteration requires a Poisson solve and five Helmholtz solves
(three momentum equations, an Enthalpy equation, and the subgrid-scale kinetic energy equation).
It is difficult to compare AMR-Wind and Nalu-Wind due to the differences in discretization and numerical
implementation. The most significant difference between the two solvers is that AMR-Wind uses structured grids
whereas Nalu-Wind uses unstructured grids. There is a lot of computational overhead with storing
and manipulating unstructured data.

>>>>

For both AMR-Wind and Nalu-Wind each time step is dominated by the linear solver work. 
A time step within AMR-Wind requires two poisson solves (MAC and nodal projection),
a tensor Helmholtz solve for Momentum equations, and two scalar Helmholtz solves 
(potential temperature equation and subgrid-scale kinetic energy equation).
Nalu-Wind is a fully implicit scheme and requires a non-linear Picard iteration for each time
step, in this work we use two Picard iterations for every time step.
Each Picard iteration requires a Poisson solve and five Helmholtz solves
(three momentum equations, an enthalpy equation, and the subgrid-scale kinetic energy equation).
It is difficult to compare AMR-Wind and Nalu-Wind due to the differences in discretization and numerical
implementation. The most significant difference between the two solvers is that AMR-Wind uses structured grids
whereas Nalu-Wind uses unstructured grids. There is a lot of computational overhead with storing
and manipulating unstructured data.
